### 2015-09-29 untitled.tex
edited untitled.tex

The basic notation in the report in \cite{Raj:suspension1991} is a \emph{deferrable task}. In Section 3 in the report in \cite{Raj:suspension1991}, it is assumed that "\emph{With deferred execution, a task $\tau_i$ can execute its $C_i$ units of execution in discrete amounts $C_i^1, C_i^2$, $\cdots$ with suspension inbetween $C_i^j$ and $C_i^{j+1}$.\footnote{The notations are alerted here to be consistent.} Without any loss of generality, we shall assume that a task $\tau_i$ can defer its entire execution time but not parts of it. hat is, a task τi executes for Ci units with no suspensions once it begins execution. Any task that does suspend after it executes for a while can be considered to be two or more tasks each with its own worst- case execution time. The only difference is that if a task $\tau_i$ is split into two tasks $\tau_i'$ followed by $\tau_i''$, then $\tau_i''$ has the same deadlines as $\tau_i′$. }".

The deferrable execution of a deferrable task imposes a scheduling penalty because one instance of a deferrable task can first defer defer its execution by some amount of time and for the next instance without any deferrable execution. The purpose of the period enforcer algorithm is to reduce such penalty. One of the main contributions in the report in \cite{Raj:suspension1991} is its Theorem 5, as follows:

\begin{quote}
{\bf Theorem 5} \cite{Raj:suspension1991}: A deferrable task that is schedulable under its worst-case conditions is also schedulable under the period enforcer algorithm.
\end{quote}

The period enforcer algorithm can only be applied for the segmented case.

>>>>

The basic notation in the report in \cite{Raj:suspension1991} is a \emph{deferrable task}. In Section 3 in the report in \cite{Raj:suspension1991}, it is assumed that "\emph{With deferred execution, a task $\tau_i$ can execute its $C_i$ units of execution in discrete amounts $C_i^1, C_i^2$, $\cdots$ with suspension inbetween $C_i^j$ and $C_i^{j+1}$.\footnote{The notations are alerted here to be consistent.} Without any loss of generality, we shall assume that a task $\tau_i$ can defer its entire execution time but not parts of it. That is, a task $\tau_i$ executes for $C_i$ units with no suspensions once it begins execution. Any task that does suspend after it executes for a while can be considered to be two or more tasks each with its own worst- case execution time. The only difference is that if a task $\tau_i$ is split into two tasks $\tau_i'$ followed by $\tau_i''$, then $\tau_i''$ has the same deadlines as $\tau_i′$. }".

The deferrable execution of a deferrable task imposes a scheduling penalty because one instance of a deferrable task can first defer defer its execution by some amount of time and for the next instance without any deferrable execution. The purpose of the period enforcer algorithm is to reduce such penalty. One of the main contributions in the report in \cite{Raj:suspension1991} is its Theorem 5, as follows:
\begin{quote}
{\bf Theorem 5} \cite{Raj:suspension1991}: A deferrable task that is schedulable under its worst-case conditions is also schedulable under the period enforcer algorithm.
\end{quote}

Theorem 5 in \cite{Raj:suspension1991} provides a very positive result to handle deferrable task systems. That is, if a deferrable task system can be schedulable by using a fixed-priority scheduling policy, the sporadic enforcer algorithm also provides a feasible schedule. However, recall that the deferrable task systems are based on the assumption that a deferrable task $\tau_i$ can defer its entire execution time but not parts of it. If we would like to use this result to handle segmented self-suspending task systems, the first question we have to answer is \emph{"What is the corresponding deferrable task system of a sporadic segmented self-suspending task system?"}. Unfortunately, the report in \cite{Raj:suspension1991} did not provide any explanation about the above question. In this report, we will explain three concepts:
\begin{itemize}
\item First, there exists (at least) a sporadic segmented self-suspending task system that is schedulable under fixed-priority scheduling without any enforcement, but the corresponding schedule by using period enforcer algorithm is not feasible. This shows that the result in Theorem 5 in \cite{Raj:suspension1991} has to be carefully used only based on the schedulability of \emph{deferrable task systems} instead of \emph{self-suspending task systems}.
\item Second, deriving the corresponding deferrable task system of a sporadic segmented self-suspending task system is an open problem to be done in polynomial time. The recent findings by Netlissen et al. \cite{ecrts15nelissen} can be applied, but it takes exponential time.
\item Third, the result in Theorem 5 in \cite{Raj:suspension1991} can be very useful for handling self-suspending task systems if there exist \emph{efficient} schedulability tests of the corresponding deferrable task systems or the period enforcer algorithm. However, there is no such schedulability test up to now.
\end{itemize}

This report will explain

\section{Mismatche of Self-Suspending Tasks and Deferrable Tasks}
